The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-16 paper/paper.Rmd
added id to individual subject plot

```{r feature-plot, fig.cap = "Summary plots to check the cleaned data reveal more cleaning is necessary: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual with an unusual wage relative to their years of data (C). Some values of hourly wages are unbelievable, and some individuals have extemely unusual wages in some years.", fig.width=6, fig.height=2}
```

>>>>

```{r feature-plot, fig.cap = "Summary plots to check the cleaned data reveal more cleaning is necessary: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual (id=39) with an unusual wage relative to their years of data (C). Some values of hourly wages are unbelievable, and some individuals have extemely unusual wages in some years.", fig.width=6, fig.height=2}
```
